---
title: "post skeleton created with new_post() function"
description: |
  This is an example of a quarto post that was generated using a very slightly modified version of Tom Mock's new_post() function
author: Simon Coulombe
date: 2024-04-17
categories: ["R", "quarto"]
lang: en
---

Everything in this `index.qmd` (except this paragraph) was generated by a slightly modified version of Tom Mock's new_post() function described on his blog, [The MockUp](https://themockup.blog/posts/2022-11-08-use-r-to-generate-a-quarto-blogpost/).  I slightly modified it to add the session info (also [his code](https://themockup.blog/posts/2022-04-18-session-info/) ) and the repository/render time.  I also added the `lang` and `categories` lines to the yaml header because I'm probably going to be switching a lot between French and English.   

:::{.callout-tip collapse="true"}
## Reproductibilité  

Ce document a été généré le `r format(Sys.time(),"%e %B %Y à %T ")`.    par le programme `r knitr::current_input()`.  Note: les fichiers `.qmd` voient leur extension remplacée par `.rmarkdown` ici.  

```{r repo, cache=FALSE, echo = FALSE}
git2r::repository()
```

```{r sessioninfo, cache = FALSE, echo = FALSE}
# save the session info as an object
library(sessioninfo)
pkg_sesh <- sessioninfo::session_info(pkgs = "attached")

# get the quarto version
quarto_version <- system("quarto --version", intern = TRUE)

# inject the quarto info
pkg_sesh$platform$quarto <- paste(
  system("quarto --version", intern = TRUE), 
  "@", 
  quarto::quarto_path()
)

# print it out
pkg_sesh
```
:::
